---
title: "Predictive Analysis"
author: "Shane Kercheval"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 3
---

```{r setup, echo = FALSE, results='hide', message=FALSE, warning=FALSE}
options(scipen=999) # non-scientific notation
options(width=180)
source('~/r-tools/output/plots.R', chdir=TRUE)
source('~/r-tools/output/markdown.R', chdir=TRUE)
library('data.table')
library(partykit) # Use the partykit package to make some nice plots. First, convert the rpart objects to party objects.
library(psych)
library(knitr)
library(scales)
library(DMwR)
library(e1071)
library(Hmisc)
library(corrplot)
library(stringr)
library(tidyverse)
library(caret)
library(randomForest)

opts_chunk$set(out.width='750px', dpi=200)

require(doMC)
registerDoMC(cores = round(detectCores()/2) + 1) # All subsequent models are then run in parallel - https://topepo.github.io/caret/parallel-processing.html

seed <- 123
refresh_models <- FALSE
```

```{r function_definition, echo = FALSE}
check_data <- function(dataset, validate_n_p = TRUE, training_tune_grid = NULL, training_method = NULL)
{
	if(validate_n_p) {
		cat('\n\n> Validating n/p...\n\n')
		number_of_samples <- nrow(dataset)
		number_of_dimensions <- ncol(dataset)
		sample_to_dimension_ratio <- number_of_samples / number_of_dimensions

		stopifnot(sample_to_dimension_ratio >= 5)
	}

	if(!is.null(training_tune_grid)) {
		cat('\n\n> Validating Tune Grid...\n\n')
		model_tuning_parameters <- as.character(modelLookup(training_method)$parameter)
		model_tuning_parameters <- model_tuning_parameters[model_tuning_parameters != 'parameter']
		stopifnot(colnames(training_tune_grid) %in% model_tuning_parameters) # make sure all the parameters passed in exist in the tuning parameters
		stopifnot(model_tuning_parameters %in% colnames(training_tune_grid)) # make sure all the tuning parameters exist in the grid
	}
}
```

```{r dataset_definition, echo = FALSE}
concrete <- fread('./regression_data/concrete.csv')
regression_dataset <- concrete %>%
	dplyr::rename(target = strength) %>%
	dplyr::select(target, everything())
regression_dataset <- as.data.frame(regression_dataset)

# insurance <- fread('./regression_data/insurance.csv')
# regression_dataset <- insurance %>%
# 	dplyr::rename(target = expenses) %>%
# 	dplyr::mutate(sex = factor(sex),
# 				  region = factor(region),
# 				  smoker = factor(smoker)) %>%
# 	dplyr::select(target, everything())
# regression_dataset <- as.data.frame(regression_dataset)
# str(regression_dataset)

#library(AppliedPredictiveModeling)
#data(abalone) # http://archive.ics.uci.edu/ml/datasets/Abalone
# regression_dataset <- abalone %>%
# 	dplyr::rename(target = Rings) %>%
# 	dplyr::select(target, everything())

set.seed(123)
regression_dataset$random1 <- sample(c(TRUE,FALSE), nrow(regression_dataset), TRUE)
set.seed(321)
regression_dataset$random2 <- sample(c(TRUE,FALSE), nrow(regression_dataset), TRUE)

###### solubility data from APM examples
# library(AppliedPredictiveModeling)
# data(solubility)
# regression_dataset <- rbind(solTrainX %>% mutate(solubility = solTrainY), solTestX %>% mutate(solubility = solTestY)) %>%
# 	rename(target = solubility) %>%
# 	dplyr::select(target, everything())
############
```

```{r dataset_prepare, echo = FALSE}
regression_dataset <- regression_dataset %>%
	#mutate_if(is.character, as.factor) %>%
	mutate_if(is.logical, as.factor)

regression_column_names <- colnames(regression_dataset)
numeric_columns <- map_lgl(regression_column_names, ~ {
	return (is.numeric(regression_dataset[, .]))
})
numeric_column_names <- regression_column_names[numeric_columns]
numeric_column_names <- numeric_column_names[numeric_column_names != 'target']

sample_size <- nrow(regression_dataset)
num_predictors <- length(regression_dataset) - 1
```

# Tuning Parameters

```{r tuning_parameters}
# train/test set
training_percentage <- 0.80

# cross validation
cross_validation_num_folds <- 10
cross_validation_num_repeats <- 3

# tuning
tuning_ridge_lambda <- seq(0, 0.1, length = 15) # Weight Decay
tuning_enet_lambda = c(0, 0.01, 0.1) # Weight Decay
tuning_enet_fraction <- seq(0.05, 1, length = 20) # Fraction of Full Solution

tuning_neural_network_decay <- c(0, 0.01, 0.1) # weight decay
tuning_neural_network_size <- c(1, 3, 5, 7, 9, 11, 13) # number of hidden units
tuning_neural_network_bag <- c(FALSE, TRUE) # bagging
parameter_neural_network_linout <- TRUE # use the linear relationship between the hidden units and the prediction (APM pg 162) i.e. linear output units
parameter_neural_network_trace <- FALSE
parameter_neural_network_max_num_weights <- 13 * (ncol(regression_dataset)) + 13 + 1 # The maximum allowable number of weights. There is no intrinsic limit in the code, but increasing MaxNWts will probably allow fits that are very slow and time-consuming.
parameter_neural_network_max_iterations <- 1000 # maximum number of iterations. Default 100

tuning_mars_degree <- 1:2 # Product Degree (of features that are added to the model)
tuning_mars_nprune <- 2:38 # number of terms retained

tuning_svm_poly_degree <- 1:2 # Polynomial Degree
tuning_svm_poly_scale <- c(0.01, 0.005, 0.001) # Scale
tuning_svm_cost <- 2^(-4:10) # Cost

tuning_ctree_mincriterion <- sort(c(0.95, seq(0.75, 0.99, length = 2)))

tuning_treebag_nbagg <- 25 # number of decision trees voting in the ensemble (default for some packages is 25)

parameter_random_forest_ntree <- 1000 # the number of bootstrap samples. althought he default is 500, at least 1,000 bootstrap samples should be used (and perhaps more depending on the number of predictors and the values of mtry).
tuning_random_forest_mtry <- unique(floor(seq(10, ncol(regression_dataset) - 1, length = 10))) # number of predictors that are randomly sampled as randidates for each split (default in regression is number of predictors divded by 3)
if(length(tuning_random_forest_mtry) == 1)
{
	tuning_random_forest_mtry <- c(round(tuning_random_forest_mtry / 2), tuning_random_forest_mtry - 1)
}

tuning_boosting_interaction_depth <- seq(1, 7, by = 2) # Boosting Iterations
tuning_boosting_n_trees <- seq(100, 1000, by = 50) # Max Tree Depth
tuning_boosting_shrinkage <- c(0.01, 0.1) # Shrinkage
tuning_boosting_min_obs_in_node <- 10 # Min. Terminal Node Size

tuning_cubist_committees <- c(1:10, 20, 50, 75, 100)
tuning_cubist_neighbors <- c(0, 1, 5, 9)
```

# Dataset

> Assumes the dataset has factors for strings; logical for TRUE/FALSE; `target` for outcome variable

## Summary

> Total predictors: ``r num_predictors``

> Total data-points/rows: ``r sample_size``

> Number of training data-points: ``r round(sample_size * training_percentage)``

Rule of thumbs for dimensions (Probabilistic and Statistical Modeling in Computer Science; pg 430):

> r < sqrt(n); where r is the number of predictors and sqrt(n) is the square root of the sample size (``r round(sqrt(sample_size))``): ``r num_predictors < round(sqrt(sample_size))``

> r < sqrt(n_t); where r is the number of predictors and sqrt(n_t) is the square root of the training set size (``r round(sqrt(round(sample_size * training_percentage)))``): ``r num_predictors < round(sqrt(round(sample_size * training_percentage)))``

```{r summary, echo = FALSE}
summary(regression_dataset)
```

## Skewness

Note: `Box-Cox` can only be applied to sets (i.e. predictors) where all values are `> 0`. So some/most/all? `NA`s will be from that limiation.

```{r skewness, echo = FALSE}
skewnewss_statistics <- map_dbl(regression_column_names, ~ {
	column_name <- .

	dataset_column <- regression_dataset[, column_name]
	if(is.numeric(dataset_column) && min(dataset_column > 0))
	{
		return (BoxCoxTrans(dataset_column)$skewness)
	}else{
		return (NA)
	}
})

kable(data.frame(column = regression_column_names, boxcox_skewness = skewnewss_statistics))
```

## Outliers

```{r outliers, echo = FALSE}
outliers <- map(regression_column_names[numeric_columns], ~ {
	numeric_data <- regression_dataset[, .]

	outlier_range <- 2 # this multipied by IQR (traditionally this number is 1.5)

	lower_quantile <- quantile(numeric_data)[2]
	upper_quantile <- quantile(numeric_data)[4]
	iqr <- upper_quantile - lower_quantile

	threshold_upper <- (iqr * outlier_range) + upper_quantile
	threshold_lower <- lower_quantile - (iqr * 1.5) # Any numeric_data point outside (> threshold_upper or < threshold_lower) these values is a mild outlier

	upper_outlier_count <- sum(numeric_data > threshold_upper)
	lower_outlier_count <- sum(numeric_data < threshold_lower)

	return (list(upper_outlier_count, lower_outlier_count))
})

outliers <- data.frame(	columns = regression_column_names[numeric_columns],
						lower_outlier_count = map_chr(outliers, ~ {.[[2]]}), 
						upper_outlier_count = map_chr(outliers, ~ {.[[1]]}))
kable(outliers)
```

## Correlation & Collinearity

### Correlation

```{r correlation, echo = FALSE, fig.height=10, fig.width=10}
if(sum(numeric_columns == TRUE) >= 2) {

	#pairs.panels(regression_dataset[, numeric_columns])
	correlations <- cor(regression_dataset[, numeric_columns])
	corrplot::corrplot(correlations, order = "hclust", tl.cex = .35, col = colorRampPalette(rev(c("#67001F", "#B2182B", "#D6604D", "#F4A582", "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE", "#4393C3", "#2166AC", "#053061")))(200))
} else {
	cat('\n\n> Not enough numberic columns for correlation.\n\n')
}
```

### Collinearity Removal

```{r removal_setup, echo = FALSE}
correlation_threshold <- 0.90
```

#### Caret's `findCorrelation`

Shows caret's recommendation of removing collinear columns based on correlation threshold of ``r correlation_threshold``

```{r caret_collinearity, echo = FALSE}
numeric_predictor_data <- regression_dataset[, numeric_columns]
numeric_predictor_data <- numeric_predictor_data %>% dplyr::select(-target) # remove target column
collinear_indexes <- findCorrelation(cor(numeric_predictor_data), correlation_threshold)
if(length(collinear_indexes) == 0)
{
	recommended_columns_caret <- colnames(regression_dataset)
}else{
	recommended_columns_caret <- c('target', colnames(numeric_predictor_data)[-collinear_indexes])	
}
```

> columns recommended for removal: ``r paste(colnames(numeric_predictor_data)[collinear_indexes], collapse = ', ')``

> final columns recommended: ``r paste(recommended_columns_caret, collapse = ', ')``

#### Heuristic

This method is described in APM pg 47 as the following steps

- calculate the correlation matrix of predictors
- determine the two predictors associated with the largest absolute pairwise correlation (call them predictors `A` and `B`)
- Determine the average correlation between `A` and the other variables.
	- Do the same for `B`
- If `A` has a larger average correlation, remove it; otherwise, remove predcitor `B`
- Repeat until no absolute correlations are above the threshold (``r correlation_threshold``)

```{r heuristic_collinearity, echo = FALSE}
predictor_correlations <- cor(numeric_predictor_data)

walk(1:nrow(predictor_correlations), ~ {
	predictor_correlations[.,.] <<- NA	
})

while(max(abs(predictor_correlations), na.rm = TRUE) > correlation_threshold) {
	## caret's findCorrelation function is used to identify columns to remove.
	num_cols_rows <- nrow(predictor_correlations)
	#highCorr <- findCorrelation(predictor_correlations, .75)
	ab_index <- which(	abs(predictor_correlations) == max(abs(predictor_correlations), na.rm = TRUE) &
						abs(predictor_correlations) > 0.75)[1] # get the first index of the highest correlation
	a_index <- ceil(ab_index / num_cols_rows) # get the row number 
	b_index <- ab_index - (num_cols_rows * (a_index-1))

	ave_a_predictor_correlations <- mean(abs(predictor_correlations[a_index, ]), na.rm = TRUE)
	ave_b_predictor_correlations <- mean(abs(predictor_correlations[b_index, ]), na.rm = TRUE)

	if(ave_a_predictor_correlations > ave_b_predictor_correlations)
	{
		predictor_correlations <<- predictor_correlations[-a_index, -a_index]
				
	}else
	{
		predictor_correlations <<- predictor_correlations[-b_index, -b_index]
	}	
	
}

recommended_numeric_columns <- colnames(predictor_correlations)
non_numeric_columns <- regression_column_names[!(regression_column_names %in% numeric_column_names)] # includes target
recommended_columns_custom <- c(non_numeric_columns, recommended_numeric_columns)
recommended_removal <- regression_column_names[!(regression_column_names %in% recommended_columns_custom)]


if(sum(numeric_columns == TRUE) >= 2) {

	predictor_correlations <- cor(numeric_predictor_data)

	walk(1:nrow(predictor_correlations), ~ {
		predictor_correlations[.,.] <<- NA	
	})

	while(max(abs(predictor_correlations), na.rm = TRUE) > correlation_threshold) {
		## caret's findCorrelation function is used to identify columns to remove.
		num_cols_rows <- nrow(predictor_correlations)
		#highCorr <- findCorrelation(predictor_correlations, .75)
		ab_index <- which(	abs(predictor_correlations) == max(abs(predictor_correlations), na.rm = TRUE) &
							abs(predictor_correlations) > 0.75)[1] # get the first index of the highest correlation
		a_index <- ceil(ab_index / num_cols_rows) # get the row number 
		b_index <- ab_index - (num_cols_rows * (a_index-1))
	
		ave_a_predictor_correlations <- mean(abs(predictor_correlations[a_index, ]), na.rm = TRUE)
		ave_b_predictor_correlations <- mean(abs(predictor_correlations[b_index, ]), na.rm = TRUE)
	
		if(ave_a_predictor_correlations > ave_b_predictor_correlations)
		{
			predictor_correlations <<- predictor_correlations[-a_index, -a_index]

		}else {

			predictor_correlations <<- predictor_correlations[-b_index, -b_index]
		}	
		
	}
	recommended_numeric_columns <- colnames(predictor_correlations)
	non_numeric_columns <- regression_column_names[!(regression_column_names %in% numeric_column_names)] # includes target
	recommended_columns_custom <- c(non_numeric_columns, recommended_numeric_columns)
	recommended_removal <- regression_column_names[!(regression_column_names %in% recommended_columns_custom)]
	
} else {

	cat('\n\n> Not enough numberic columns for collinearity. Not removing any columns.\n\n')
	recommended_columns_custom <- regression_column_names
	recommended_removal <- ''
}
```

> columns recommended for removal: ``r paste(recommended_removal, collapse = ', ')``

> final columns recommended: ``r paste(recommended_columns_custom, collapse = ', ')``

## Graphs

```{r graphs, echo = FALSE, fig.height=4, fig.width=6, comment='', results='asis'}
df_data <- data.frame(target=regression_dataset$target)
fun_args <- list(mean = mean(df_data$target), sd = sd(df_data$target))
quantiles <- quantile(df_data$target, c(0.02, 0.98)) # cut off any 'outliers' (crude) so it doesn't skew graph
ggplot(data = df_data, mapping = aes(x = target)) +
	geom_histogram(mapping=aes(y = ..density..), bins = 30) + # histogram of data
	geom_density(col = "red") + # emperical PDF
	stat_function(fun = dnorm, args = fun_args, col = "blue") + # theoretical normal PDF, based on data's mean & standard deviation
	coord_cartesian(xlim = c(quantiles[1], quantiles[2]))

ggplot(data = df_data, mapping = aes(x = 'target',  y = target, group = 1)) +
	geom_boxplot()

walk(regression_column_names, ~ {
	column_name <- .
	
	if(column_name == 'target')
	{
		return ()
	}

	cat(paste('\n\n###', column_name, '\n\n'))
	dataset_column <- regression_dataset[, column_name]
	if(is.numeric(dataset_column))
	{
		df_data <- data.frame(continuous_variable=dataset_column)
		fun_args <- list(mean = mean(df_data$continuous_variable), sd = sd(df_data$continuous_variable))
		quantiles <- quantile(df_data$continuous_variable, c(0.02, 0.98)) # cut off any 'outliers' (crude) so it doesn't skew graph
		
		result = tryCatch({
			print(ggplot(data = df_data, mapping = aes(x = continuous_variable)) +
				geom_histogram(mapping=aes(y = ..density..), bins = 30) + # histogram of data
				geom_density(col = "red") + # emperical PDF
				stat_function(fun = dnorm, args = fun_args, col = "blue") + # theoretical normal PDF, based on data's mean & standard deviation
				coord_cartesian(xlim = c(quantiles[1], quantiles[2])) + labs(x = column_name))

		}, error = function(e) {
			cat('\n\nError with histogram.\n\n')
		})
		
		print(ggplot(data = df_data, mapping = aes(x = column_name,  y = continuous_variable, group = 1)) +
			geom_boxplot())

		print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column, y = target)) +
			geom_point(alpha=0.2) + # alpha avoids overfiting
			labs(x = column_name))

		print(ggplot(data = regression_dataset) +
			geom_hex(mapping = aes(x = dataset_column, y = target)) + 
			labs(x = column_name))
		
		result = tryCatch({
			print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column, y = target)) +
					geom_boxplot(mapping = aes(group = cut_number(dataset_column, 10))) + 
					labs(x = column_name))
		}, error = function(e) {
			cat('\n\nError with boxplot.\n\n')
		})

	}else if(is.factor(dataset_column)){
		
		print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column)) + 
			geom_bar(mapping=aes(fill = dataset_column)) + 
			ggtitle(paste('Histogram of', column_name)) + ylab('Count') + xlab(column_name) +
			theme(axis.text.x = element_text(angle = 50, hjust = 1)) + guides(fill = FALSE))

		print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column, y = target)) +
			geom_boxplot(mapping = aes(group = dataset_column)) + 
			labs(x = column_name))

	}else if(is.logical(dataset_column)){
		print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column)) + 
			geom_bar(mapping=aes(fill = dataset_column)) + 
			ggtitle(paste('Histogram of', column_name)) + ylab('Count') + xlab(column_name) +
			theme(axis.text.x = element_text(angle = 50, hjust = 1)) + guides(fill = FALSE))

		print(ggplot(data = regression_dataset, mapping = aes(x = dataset_column, y = target)) +
			geom_boxplot(mapping = aes(group = dataset_column)) + 
			labs(x = column_name))
	}else{
		stop(paste('unknown data type -', column_name))
	}
})
```

# Spot-Check

```{r spot_check_prepare_numeric, echo = FALSE}
set.seed(seed)
training_index <- createDataPartition(regression_dataset$target, p = training_percentage, list = TRUE)
regression_train <- regression_dataset[training_index$Resample1, ]
regression_test <- regression_dataset[-training_index$Resample1, ]

df_target_long <- data.frame(	type = rep('regression_dataset', times = nrow(regression_dataset)),
								target = regression_dataset$target)
df_target_long <- rbind(df_target_long, data.frame(	type = rep(	'regression_train',
																times = nrow(regression_train)),
													target = regression_train$target))
df_target_long <- rbind(df_target_long, data.frame(	type = rep(	'regression_test',
																times = nrow(regression_test)),
													target = regression_test$target))
ggplot(data = df_target_long, mapping = aes(x = type,  y = target, group = type)) +
	geom_boxplot()
```

> Using ``r cross_validation_num_folds``-fold cross-validation with ``r cross_validation_num_repeats`` repeats.

- Note: e.g. if there are rare values at the target extremes (lows/highs), the train and especially the test set might not be training/testing on them. Is the test set representative? If the test set doesn't have as extreme values, it can even predict better (e.g. lower RMSE higher Rsquared) than the average Cross Validation given on training because it's not using those extreme values.

> used ``r percent(training_percentage)`` of data for `training` set (``r nrow(regression_train)``), and ``r percent(1 - training_percentage)`` for `test` set (``r nrow(regression_test)``).

```{r spot_check_numeric, echo = FALSE}
# we have to make sure they are fit on exactly the same test sets in training and cross validation so we are sure we are making an apples-to-apples comparison
set.seed(seed)
spot_check_folds <- createMultiFolds(	regression_train$target,
										k = cross_validation_num_folds,
										times = cross_validation_num_repeats) # maintains the `churn` ratio

train_control <- trainControl(
	method = 'repeatedcv',
	number = cross_validation_num_folds,
	repeats = cross_validation_num_repeats,
	verboseIter = FALSE,
	savePredictions = TRUE,
	index = spot_check_folds)
```

### Linear Regression - no pre processing

```{r linear_regression_no_pre_processing, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_no_pre_processing <- train(	target ~ .,
									data = regression_train,
									method = 'lm',
									trControl = train_control)

	saveRDS(lm_no_pre_processing, file = './regression_data/lm_no_pre_processing.RDS')
} else{
	lm_no_pre_processing <- readRDS('./regression_data/lm_no_pre_processing.RDS')
}
summary(lm_no_pre_processing)
plot(lm_no_pre_processing$finalModel)
```

### Linear Regression - basic pre processing

```{r linear_regression_basic_pre_processing, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_basic_pre_processing <- train(	target ~ .,
										data = regression_train,
										method = 'lm',
										trControl = train_control,
										preProc=c('center', 'scale', 'knnImpute'))

	saveRDS(lm_basic_pre_processing, file = './regression_data/lm_basic_pre_processing.RDS')
} else{
	lm_basic_pre_processing <- readRDS('./regression_data/lm_basic_pre_processing.RDS')
}
summary(lm_basic_pre_processing)
plot(lm_basic_pre_processing$finalModel)
```

### Linear Regression - basic pre processing with medianImpute

```{r linear_regression_impute, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_median_impute <- train(	target ~ .,
								data = regression_train,
								method = 'lm',
								trControl = train_control,
								preProc=c('center', 'scale', 'medianImpute'))

	saveRDS(lm_median_impute, file = './regression_data/lm_median_impute.RDS')
} else{
	lm_median_impute <- readRDS('./regression_data/lm_median_impute.RDS')
}
summary(lm_median_impute)
plot(lm_median_impute$finalModel)
```

### Linear Regression - basic pre processing

```{r linear_regression_basic, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_near_zero_variance <- train(	target ~ .,
									data = regression_train,
									method = 'lm',
									trControl = train_control,
									preProc=c('nzv', 'center', 'scale', 'knnImpute')) # APM pg 550

	saveRDS(lm_near_zero_variance, file = './regression_data/lm_near_zero_variance.RDS')
} else{
	lm_near_zero_variance <- readRDS('./regression_data/lm_near_zero_variance.RDS')
}
summary(lm_near_zero_variance)
plot(lm_near_zero_variance$finalModel)
```

### Linear Regression - skewness - YeoJohnson

```{r linear_regression_YeoJohnson, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_skewness_y <- train(	target ~ .,
							data = regression_train,
							method = 'lm',
							trControl = train_control,
							preProc=c('YeoJohnson', 'center', 'scale', 'knnImpute')) # (caret docs: 'The Yeo-Johnson transformation is similar to the Box-Cox model but can accommodate predictors with zero and/or negative values (while the predictors values for the Box-Cox transformation must be strictly positive.) ')

	saveRDS(lm_skewness_y, file = './regression_data/lm_skewness_y.RDS')
} else{
	lm_skewness_y <- readRDS('./regression_data/lm_skewness_y.RDS')
}
summary(lm_skewness_y)
plot(lm_skewness_y$finalModel)
```

### Linear Regression - skewness - BoxCox

```{r linear_regression_BoxCox, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_skewness_bc <- train(target ~ .,
							data = regression_train,
							method = 'lm',
							trControl = train_control,
							preProc=c('BoxCox', 'center', 'scale', 'knnImpute')) # (caret docs: 'The Yeo-Johnson transformation is similar to the Box-Cox model but can accommodate predictors with zero and/or negative values (while the predictors values for the Box-Cox transformation must be strictly positive.) ')

	saveRDS(lm_skewness_bc, file = './regression_data/lm_skewness_bc.RDS')
} else{
	lm_skewness_bc <- readRDS('./regression_data/lm_skewness_bc.RDS')
}
summary(lm_skewness_bc)
plot(lm_skewness_bc$finalModel)
```

### Linear Regression - remove collinear data - based on caret's recommendation

```{r linear_regression_collinear_caret, echo = FALSE}
if(refresh_models) {
	check_data(regression_train[, recommended_columns_caret], validate_n_p = TRUE)

	set.seed(seed)
	lm_remove_collinearity_caret <- train(	target ~ .,
											data = regression_train[, recommended_columns_caret],
											method = 'lm',
											trControl = train_control,
											preProc=c('nzv', 'center', 'scale', 'knnImpute')) # APM pg 550

	saveRDS(lm_remove_collinearity_caret, file = './regression_data/lm_remove_collinearity_caret.RDS')
} else{
	lm_remove_collinearity_caret <- readRDS('./regression_data/lm_remove_collinearity_caret.RDS')
}
summary(lm_remove_collinearity_caret)
plot(lm_remove_collinearity_caret$finalModel)
```

### Linear Regression - remove collinear data - based on calculation

```{r linear_regression_collinear_calc, echo = FALSE}
if(refresh_models) {
	check_data(regression_train[, recommended_columns_custom], validate_n_p = TRUE)

	set.seed(seed)
	lm_remove_collinearity_custom <- train(	target ~ .,
											data = regression_train[, recommended_columns_custom],
											method = 'lm',
											trControl = train_control,
											preProc=c('nzv', 'center', 'scale', 'knnImpute')) # APM pg 550

	saveRDS(lm_remove_collinearity_custom, file = './regression_data/lm_remove_collinearity_custom.RDS')
} else{
	lm_remove_collinearity_custom <- readRDS('./regression_data/lm_remove_collinearity_custom.RDS')
}
summary(lm_remove_collinearity_custom)
plot(lm_remove_collinearity_custom$finalModel)
```

### Robust Linear Regression

```{r robust_linear, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_robust <- train(	target ~ .,
						data = regression_train,
						method = 'rlm',
						trControl = train_control,
						preProc=c('YeoJohnson', 'center', 'scale', 'knnImpute', 'pca')) # by default uses the 'Huber' approach. (APM pg 130.) 'The Huber function uses the squared residuals when they are 'small' and the simple difference between the observed and predicted values values when the residuals are above a threshold.' (APM pg 109f)

	saveRDS(lm_robust, file = './regression_data/lm_robust.RDS')
} else{
	lm_robust <- readRDS('./regression_data/lm_robust.RDS')
}
summary(lm_robust)
plot(lm_robust$finalModel)
```

### Linear Regression - spatial sign

```{r linear_regression_spatial_sign, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = TRUE)

	set.seed(seed)
	lm_spatial_sign <- train(	target ~ .,
								data = regression_train,
								method = 'lm',
								trControl = train_control,
								preProc=c('center', 'scale', 'knnImpute', 'spatialSign'))

	saveRDS(lm_spatial_sign, file = './regression_data/lm_spatial_sign.RDS')
} else{
	lm_spatial_sign <- readRDS('./regression_data/lm_spatial_sign.RDS')
}
summary(lm_spatial_sign)
plot(lm_spatial_sign$finalModel)
```

### Linear Regression - principal components analysis

```{r linear_regression_PCA, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	lm_pca <- train(target ~ .,
					data = regression_train,
					method = 'lm',
					trControl = train_control,
					preProc=c('YeoJohnson', 'center', 'scale', 'knnImpute', 'pca')) # (APM pg 37 'to help PCA avoid summarizing distributional differences and predictor scale informatino, it is best to first transform skewed predictors and then center and scale the predictors prior to performing PCA. Centering and scaling enables PCA to find the underlying relationships in the data without being influenced by the original measurement scales.')

	saveRDS(lm_pca, file = './regression_data/lm_pca.RDS')
} else{
	lm_pca <- readRDS('./regression_data/lm_pca.RDS')
}
summary(lm_pca)
plot(lm_pca$finalModel)
```

### Principal Component Regression

```{r principal_component_PCR, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	lm_pcr <- train(target ~ ., 
					data = regression_train,
					method = 'pcr',
					trControl = train_control,
					tuneLength = 20,
					preProc = c('center', 'scale', 'knnImpute'))

	saveRDS(lm_pcr, file = './regression_data/lm_pcr.RDS')
} else{
	lm_pcr <- readRDS('./regression_data/lm_pcr.RDS')
}
summary(lm_pcr)
plot(lm_pcr)
```

### Partial Least Squares

```{r partial_least_squares, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	lm_pls <- train(target ~ .,
					data = regression_train,
					method = 'pls',
					trControl = train_control,
					preProc = c('center', 'scale', 'knnImpute'), tuneLength = 14)

	saveRDS(lm_pls, file = './regression_data/lm_pls.RDS')
} else{
	lm_pls <- readRDS('./regression_data/lm_pls.RDS')
}
summary(lm_pls)
# loadings(lm_pls$finalModel)
# scores(lm_pls$finalModel)
plot(lm_pls)

# Compare # of components of PCR vs. PLS
xyplot(RMSE ~ ncomp,data = rbind(	lm_pls$results %>% mutate(Model = 'PLS'), 
									lm_pcr$results %>% mutate(Model = 'PCR')),
					xlab = '# Components',
					ylab = 'RMSE (Cross-Validation)',
					auto.key = list(columns = 2),
					groups = Model,
					type = c('o', 'g'))
```

### Ridge Regression

```{r ridge_regression, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(lambda = tuning_ridge_lambda)
	check_data(	dataset = regression_train,
				validate_n_p = TRUE,
				training_tune_grid = training_tune_grid,
				training_method = 'ridge')

	set.seed(seed)
	lm_ridge <- train(	target ~ .,
						data = regression_train,
						method = 'ridge',
						tuneGrid = training_tune_grid,
						trControl = train_control,
						preProc = c('center', 'scale', 'knnImpute'))

	saveRDS(lm_ridge, file = './regression_data/lm_ridge.RDS')
} else{
	lm_ridge <- readRDS('./regression_data/lm_ridge.RDS')
}
summary(lm_ridge)
plot(lm_ridge)
```

### ridge & lasso combo

```{r ridge_lasso, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(lambda = tuning_enet_lambda, fraction = tuning_enet_fraction)
	check_data( dataset = regression_train,
				validate_n_p = TRUE,
				training_tune_grid = training_tune_grid,
				training_method = 'enet')

	set.seed(seed)
	lm_enet <- train(	target ~ .,
						data = regression_train,
						method = 'enet',
						tuneGrid = training_tune_grid,
						trControl = train_control,
						preProc = c('center', 'scale', 'knnImpute'))

	saveRDS(lm_enet, file = './regression_data/lm_enet.RDS')
} else{
	lm_enet <- readRDS('./regression_data/lm_enet.RDS')
}
#lm_enet$finalModel
summary(lm_enet)
plot(lm_enet)
```

### neural network - basic

```{r neural_network_basic, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(decay = tuning_neural_network_decay, size = tuning_neural_network_size)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'nnet')

	set.seed(seed)
	nlm_neur_net_basic <- train(target ~ .,
								data = regression_train,
								method = 'nnet',
								tuneGrid = training_tune_grid,
								trControl = train_control,
								preProc = c('nzv', 'center', 'scale', 'knnImpute'),
								linout = parameter_neural_network_linout,
								trace = parameter_neural_network_trace,
								MaxNWts = parameter_neural_network_max_num_weights,
								maxit = parameter_neural_network_max_iterations)

	saveRDS(nlm_neur_net_basic, file = './regression_data/nlm_neur_net_basic.RDS')
} else{
	nlm_neur_net_basic <- readRDS('./regression_data/nlm_neur_net_basic.RDS')
}
summary(nlm_neur_net_basic$finalModel)
plot(nlm_neur_net_basic)
```

### neural network - basic - removing correlated predictors

```{r neural_network_basic_removing_correlated_predictors, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(decay = tuning_neural_network_decay, size = tuning_neural_network_size)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'nnet')

	set.seed(seed)
	nlm_neur_net_basic_remove_corr <- train(target ~ .,
											data = regression_train[, recommended_columns_caret],
											method = 'nnet',
											tuneGrid = training_tune_grid,
											trControl = train_control,
											preProc = c('nzv', 'center', 'scale', 'knnImpute'),
											linout = parameter_neural_network_linout,
											trace = parameter_neural_network_trace,
											MaxNWts = parameter_neural_network_max_num_weights,
											maxit = parameter_neural_network_max_iterations)

	saveRDS(nlm_neur_net_basic_remove_corr, file = './regression_data/nlm_neur_net_basic_remove_corr.RDS')
} else{
	nlm_neur_net_basic_remove_corr <- readRDS('./regression_data/nlm_neur_net_basic_remove_corr.RDS')
}
summary(nlm_neur_net_basic_remove_corr$finalModel)
plot(nlm_neur_net_basic_remove_corr)
```

### neural network - model averaging - removing correlated predictors

```{r neural_network_averaging_removing_correlated_predictors, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(	decay = tuning_neural_network_decay,
										size = tuning_neural_network_size,
										bag = tuning_neural_network_bag)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'avNNet')

	set.seed(seed)
	nlm_neur_net_averaging_remove_corr <- train(target ~ .,
												data = regression_train[, recommended_columns_caret],
												method = 'avNNet',
												tuneGrid = training_tune_grid,
												trControl = train_control,
												preProc = c('nzv', 'center', 'scale', 'knnImpute'),
												linout = parameter_neural_network_linout,
												trace = parameter_neural_network_trace,
												MaxNWts = parameter_neural_network_max_num_weights,
												maxit = parameter_neural_network_max_iterations)

	saveRDS(nlm_neur_net_averaging_remove_corr, file = './regression_data/nlm_neur_net_averaging_remove_corr.RDS')
} else{
	nlm_neur_net_averaging_remove_corr <- readRDS('./regression_data/nlm_neur_net_averaging_remove_corr.RDS')
}
nlm_neur_net_averaging_remove_corr$finalModel
summary(nlm_neur_net_averaging_remove_corr$finalModel)
plot(nlm_neur_net_averaging_remove_corr)
```

### neural network - model averaging - PCA

```{r neural_network_averaging_PCA, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(	decay = tuning_neural_network_decay,
										size = tuning_neural_network_size,
										bag = tuning_neural_network_bag)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'avNNet')

	set.seed(seed)
	nlm_neur_net_averaging_pca <- train(target ~ .,
										data = regression_train,
										method = 'avNNet',
										tuneGrid = training_tune_grid,
										trControl = train_control,
										preProc = c('nzv', 'YeoJohnson', 'center', 'scale', 'knnImpute', 'pca'),
										linout = parameter_neural_network_linout,
										trace = parameter_neural_network_trace,
										MaxNWts = parameter_neural_network_max_num_weights,
										maxit = parameter_neural_network_max_iterations)

	saveRDS(nlm_neur_net_averaging_pca, file = './regression_data/nlm_neur_net_averaging_pca.RDS')
} else{
	nlm_neur_net_averaging_pca <- readRDS('./regression_data/nlm_neur_net_averaging_pca.RDS')
}
summary(nlm_neur_net_averaging_pca$finalModel)
plot(nlm_neur_net_averaging_pca)
```

### MARS (Multivariate Adaptive Regression Splines)

```{r mars, echo = FALSE, fig.height=6, fig.width=9}
if(refresh_models) {
	training_tune_grid <- expand.grid(degree = tuning_mars_degree, nprune = tuning_mars_nprune)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'earth')

	set.seed(seed)
	nlm_mars <- train(	target ~ .,
						data = regression_train,
						method = 'earth',
						tuneGrid = training_tune_grid,
						trControl = train_control)

	saveRDS(nlm_mars, file = './regression_data/nlm_mars.RDS')
} else{
	nlm_mars <- readRDS('./regression_data/nlm_mars.RDS')
}
#nlm_mars$finalModel
summary(nlm_mars$finalModel)
plot(nlm_mars)
require(earth)
plotmo(nlm_mars$finalModel)
#marsImp <- varImp(nlm_mars, scale = FALSE)
#plot(marsImp, top = 25)
```

### SVM - Support Vector Machine - Radial

```{r svm_radial, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	nlm_svm_radial <- train(target ~ .,
							data = regression_train,
							method = 'svmRadial',
							preProc = c('center', 'scale', 'knnImpute'),
							tuneLength = 14, # tuneLength tunes C (sigma is chosen automatically)
							trControl = train_control)

	saveRDS(nlm_svm_radial, file = './regression_data/nlm_svm_radial.RDS')
} else{
	nlm_svm_radial <- readRDS('./regression_data/nlm_svm_radial.RDS')
}
nlm_svm_radial$finalModel
plot(nlm_svm_radial, scales = list(x = list(log = 2)))
```

### SVM - Support Vector Machine - Linear

```{r svm_linear, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- data.frame(C=tuning_svm_cost)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'svmLinear')

	set.seed(seed)
	nlm_svm_linear <- train(target ~ .,
							data = regression_train,
							method = 'svmLinear',
							preProc = c('center', 'scale', 'knnImpute'),
							tuneGrid = training_tune_grid,
							trControl = train_control)

	saveRDS(nlm_svm_linear, file = './regression_data/nlm_svm_linear.RDS')
} else{
	nlm_svm_linear <- readRDS('./regression_data/nlm_svm_linear.RDS')
}
nlm_svm_linear$finalModel
plot(nlm_svm_linear, scales = list(x = list(log = 2)))
```

### SVM - Support Vector Machine - Polynomial

```{r svm_poly, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(	degree = tuning_svm_poly_degree,
										scale = tuning_svm_poly_scale,
										C = tuning_svm_cost)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'svmPoly')

	set.seed(seed)
	nlm_svm_poly <- train(	target ~ .,
							data = regression_train,
							method = 'svmPoly',
							preProc = c('center', 'scale', 'knnImpute'),
							tuneGrid = training_tune_grid,
							trControl = train_control)

	saveRDS(nlm_svm_poly, file = './regression_data/nlm_svm_poly.RDS')
} else{
	nlm_svm_poly <- readRDS('./regression_data/nlm_svm_poly.RDS')
}
nlm_svm_poly$finalModel
plot(nlm_svm_poly, scales = list(x = list(log = 2),  between = list(x = .5, y = 1)))
```

### CART - Classification and Regression Tree - Tuning over maximum depth

```{r cart, echo = FALSE, fig.height=6, fig.width=9}
if(refresh_models) {
	check_data(	dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	tree_cart <- train(	target ~ .,
						data = regression_train,
						method = 'rpart',
						tuneLength = 25,
						trControl = train_control) # tuneLength tunes `cp` (Complexity Parameter)

	saveRDS(tree_cart, file = './regression_data/tree_cart.RDS')
} else{
	tree_cart <- readRDS('./regression_data/tree_cart.RDS')
}
tree_cart$finalModel
plot(tree_cart) # Plot the tuning results
party_tree <- as.party(tree_cart$finalModel)
plot(party_tree)
```

### CART - Classification and Regression Tree - Tuning over maximum depth

```{r cart2, echo = FALSE, fig.height=6, fig.width=9}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	tree_cart2 <- train(target ~ .,
						data = regression_train,
						method = 'rpart2',
						tuneLength = 25,
						trControl = train_control) # tuneLength tunes `maxdepth` (Max Tree Depth)

	saveRDS(tree_cart2, file = './regression_data/tree_cart2.RDS')
} else{
	tree_cart2 <- readRDS('./regression_data/tree_cart2.RDS')
}
tree_cart2$finalModel
plot(tree_cart2)
party_tree <- as.party(tree_cart2$finalModel)
plot(party_tree)
```

### Conditional Inference Tree

```{r conditional_inference, echo = FALSE, fig.height=6, fig.width=9}
if(refresh_models) {
	training_tune_grid <- data.frame(mincriterion = tuning_ctree_mincriterion)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'ctree')

	set.seed(seed)
	tree_cond_inference <- train(	target ~ .,
									data = regression_train,
									method = 'ctree',
									tuneGrid = training_tune_grid,
									trControl = train_control)

	saveRDS(tree_cond_inference, file = './regression_data/tree_cond_inference.RDS')
} else{
	tree_cond_inference <- readRDS('./regression_data/tree_cond_inference.RDS')
}
tree_cond_inference$finalModel
plot(tree_cond_inference)
plot(tree_cond_inference$finalModel)
```

### Conditional Inference Tree - Tuning over maximum depth

```{r conditional_inference2, echo = FALSE, fig.height=6, fig.width=9}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	tree_cond_inference2 <- train(	target ~ .,
									data = regression_train,
									method = 'ctree2',
									tuneLength = 25, # tuneLength tunes `maxdepth` (Max Tree Depth)
									trControl = train_control)

	saveRDS(tree_cond_inference2, file = './regression_data/tree_cond_inference2.RDS')
} else{
	tree_cond_inference2 <- readRDS('./regression_data/tree_cond_inference2.RDS')
}
tree_cond_inference2$finalModel
plot(tree_cond_inference2) # Plot the tuning results
plot(tree_cond_inference2$finalModel)
```

### Model Trees - M5

> This model is failing (not only for me, try in the future, seems like a problem in RWeka): https://github.com/topepo/caret/issues/618

```{r model_trees_m5, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	tree_m5 <- train(	target ~ .,
						data = regression_train,
						method = 'M5',
						tuneLength = 25, # tuneLength tunes `maxdepth` (Max Tree Depth)
						trControl = train_control, trace = FALSE)

	saveRDS(tree_m5, file = './regression_data/tree_m5.RDS')
} else{
	tree_m5 <- readRDS('./regression_data/tree_m5.RDS')
}
tree_m5$finalModel
plot(tree_m5) # Plot the tuning results
plot(tree_m5$finalModel)
```

### Model Trees - M5 Rules

> This model is failing (not only for me, try in the future, seems like a problem in RWeka): https://github.com/topepo/caret/issues/618

```{r model_trees_m5rules, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	tree_m5rules <- train(	target ~ .,
							data = regression_train,
							method = 'M5Rules',
							tuneLength = 25, # tuneLength tunes `maxdepth` (Max Tree Depth)
							trControl = train_control,
							trace = FALSE)

	saveRDS(tree_m5rules, file = './regression_data/tree_m5rules.RDS')
} else{
	tree_m5rules <- readRDS('./regression_data/tree_m5rules.RDS')
}
tree_m5rules$finalModel
plot(tree_m5rules) # Plot the tuning results
plot(tree_m5rules$finalModel)
```

### Bagged Trees

```{r bagged_trees, echo = FALSE}
if(refresh_models) {
	check_data(dataset = regression_train, validate_n_p = FALSE)

	set.seed(seed)
	ensemble_bagged_tree <- train(	target ~ .,
									data = regression_train,
									method = 'treebag',
									nbagg = tuning_treebag_nbagg,
									trControl = train_control)

	saveRDS(ensemble_bagged_tree, file = './regression_data/ensemble_bagged_tree.RDS')
} else{
	ensemble_bagged_tree <- readRDS('./regression_data/ensemble_bagged_tree.RDS')
}
ensemble_bagged_tree
summary(ensemble_bagged_tree)
```

### Random Forest

```{r random_forest, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- data.frame(mtry = tuning_random_forest_mtry)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'rf')

	set.seed(seed)
	ensemble_random_forest <- train(target ~ .,
									data = regression_train,
									method = 'rf',
									tuneGrid = training_tune_grid,
									ntree = parameter_random_forest_ntree,
									trControl = train_control,
									preProc=c('knnImpute'))

	saveRDS(ensemble_random_forest, file = './regression_data/ensemble_random_forest.RDS')
} else{
	ensemble_random_forest <- readRDS('./regression_data/ensemble_random_forest.RDS')
}
ensemble_random_forest
#ensemble_random_forest$finalModel
summary(ensemble_random_forest$finalModel)
plot(ensemble_random_forest)
```

### Random Forest - Conditional Inference

```{r random_forest_cond_inf, echo = FALSE, eval=FALSE, include=FALSE}
if(refresh_models) {
	training_tune_grid <- data.frame(mtry = tuning_random_forest_mtry)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'cforest')

	set.seed(seed)
	ensemble_random_forest_cond_inf <- train(	target ~ .,
												data = regression_train,
												method = 'cforest',
												tuneGrid = training_tune_grid,
												controls = cforest_unbiased(ntree = parameter_random_forest_ntree),
												trControl = train_control)

	saveRDS(ensemble_random_forest_cond_inf, file = './regression_data/ensemble_random_forest_cond_inf.RDS')
} else{
	ensemble_random_forest_cond_inf <- readRDS('./regression_data/ensemble_random_forest_cond_inf.RDS')
}
ensemble_random_forest_cond_inf
#ensemble_random_forest_cond_inf$finalModel
summary(ensemble_random_forest_cond_inf)
summary(ensemble_random_forest_cond_inf$finalModel)
plot(ensemble_random_forest_cond_inf)
```

### Boosting

```{r boosting, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(	interaction.depth = tuning_boosting_interaction_depth,
										n.trees = tuning_boosting_n_trees,
										shrinkage = tuning_boosting_shrinkage,
										n.minobsinnode = tuning_boosting_min_obs_in_node)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'gbm')

	set.seed(seed)
	ensemble_boosting <- train(	target ~ .,
								data = regression_train,
								method = 'gbm',
								tuneGrid = training_tune_grid,
								trControl = train_control,
								verbose = FALSE)

	saveRDS(ensemble_boosting, file = './regression_data/ensemble_boosting.RDS')
} else{
	ensemble_boosting <- readRDS('./regression_data/ensemble_boosting.RDS')
}
# ensemble_boosting
# ensemble_boosting$finalModel
summary(ensemble_boosting)
summary(ensemble_boosting$finalModel)
plot(ensemble_boosting)
```

### Cubist

```{r cubist, echo = FALSE}
if(refresh_models) {
	training_tune_grid <- expand.grid(	committees = tuning_cubist_committees,
										neighbors = tuning_cubist_neighbors)
	check_data(	dataset = regression_train,
				validate_n_p = FALSE,
				training_tune_grid = training_tune_grid,
				training_method = 'cubist')

	set.seed(seed)
	ensemble_cubist <- train(target ~ .,
							data = regression_train,
							method = 'cubist',
							tuneGrid = training_tune_grid,
							trControl = train_control)

	saveRDS(ensemble_cubist, file = './regression_data/ensemble_cubist.RDS')
} else{
	ensemble_cubist <- readRDS('./regression_data/ensemble_cubist.RDS')
}
# ensemble_cubist
# ensemble_cubist$finalModel
summary(ensemble_cubist)
summary(ensemble_cubist$finalModel)
plot(ensemble_cubist)
plot(ensemble_cubist, auto.key = list(columns = 4, lines = TRUE))
```

## Resamples & Top Models

### Resamples

```{r resamples_regression, echo=FALSE, fig.height=6, fig.width=9}
numeric_models <- list(
		lm_no_pre_processing = lm_no_pre_processing,
		lm_basic_pre_processing = lm_basic_pre_processing,
		lm_median_impute = lm_median_impute,
		lm_near_zero_variance = lm_near_zero_variance,
		lm_skewness_y = lm_skewness_y,
		lm_skewness_bc = lm_skewness_bc,
		lm_remove_collinearity_caret = lm_remove_collinearity_caret,
		lm_remove_collinearity_custom = lm_remove_collinearity_custom,
		lm_robust = lm_robust,
		lm_spatial_sign = lm_spatial_sign,
		lm_pca = lm_pca,
		lm_pcr = lm_pcr,
		lm_pls = lm_pls,
		lm_ridge = lm_ridge,
		lm_enet = lm_enet,
		# nlm_neur_net_basic = nlm_neur_net_basic,
		# nlm_neur_net_basic_remove_corr = nlm_neur_net_basic_remove_corr,
		# nlm_neur_net_averaging_remove_corr = nlm_neur_net_averaging_remove_corr,
		nlm_neur_net_averaging_pca = nlm_neur_net_averaging_pca,
		nlm_mars = nlm_mars,
		nlm_svm_radial = nlm_svm_radial,
		nlm_svm_linear = nlm_svm_linear,
		nlm_svm_poly = nlm_svm_poly,
		tree_cart = tree_cart,
		tree_cart2 = tree_cart2,
		tree_cond_inference = tree_cond_inference,
		tree_cond_inference2 = tree_cond_inference2,
		# tree_m5 = tree_m5,
		# tree_m5rules = tree_m5rules,
		ensemble_bagged_tree = ensemble_bagged_tree,
		ensemble_random_forest = ensemble_random_forest,
		# ensemble_random_forest_cond_inf = ensemble_random_forest_cond_inf,
		ensemble_boosting = ensemble_boosting, 
		ensemble_cubist = ensemble_cubist
		)

resamples <- resamples(numeric_models)

# Table comparison
(resamples_summary <- summary(resamples))

resamples_long <- resamples$values %>%
	dplyr::select(-Resample) %>%
	gather(type, value) %>%
	separate(col=type, into=c('model', 'metric'), sep = '~') %>%
	mutate(	model = factor(model, levels = rev(resamples$models)),
			metric = factor(metric, levels = c('RMSE', 'Rsquared')))

resamples_means <- resamples_long %>%
	dplyr::group_by(model, metric) %>%
	dplyr::summarise(average = mean(value)) %>%
	dplyr::ungroup()

min_rmse_mean <- min(resamples_means %>% filter(metric == 'RMSE') %>% dplyr::select(average))
max_rsquared_mean <- max(resamples_means %>% filter(metric == 'Rsquared') %>% dplyr::select(average))

best_values <- data.frame(metric = levels(resamples_long$metric), Z = c(min_rmse_mean, max_rsquared_mean))
ggplot(data = resamples_long, mapping = aes(x = model, y = value)) +
	geom_boxplot() + 
	stat_summary(fun.y=mean, colour="red", geom="point", shape=21, size=3, show.legend = FALSE) + 
	geom_hline(data = best_values, aes(yintercept = Z), color='red') +
	facet_grid(. ~ metric, scales = "free", space = "free_y") +
	coord_flip()
#boxplot comparison
#bwplot(resamples, metric = 'Rsquared')
#bwplot(resamples, metric = 'RMSE')
densityplot(resamples, metric = 'RMSE')
densityplot(resamples, metric = 'Rsquared')
```

### Top Models

- TODO: some models have duplicate results (e.g. different pre-processing, same results) so i'm potentially grabbing dups, and therefore < 5 different modelss

```{r definitions, echo = FALSE}
MAE <- function(actual, predicted)
{
	return (mean(abs(actual - predicted)))
}

RMSE <- function(actual, predicted)
{
	return (sqrt(mean((actual - predicted)^2)))
}
model_plots <- function(model, testing_set){

	predictions <- predict(model, newdata = testing_set %>% dplyr::select(-target))
	predicted_vs_actual <- data.frame(	obs = as.numeric(testing_set$target),
										pred = as.numeric(predictions),
										residuals = as.numeric(testing_set$target - predictions))
	
	model_rmse <- RMSE(actual = predicted_vs_actual$obs, predicted = predicted_vs_actual$pred)
	model_mae <- MAE(actual = predicted_vs_actual$obs, predicted = predicted_vs_actual$pred)
	model_correlation <- cor(x = predicted_vs_actual$obs, y = predicted_vs_actual$pred)
	
	cat(paste0('\n\n> Model RMSE: `', round(model_rmse, 4), '`\n\n'))
	cat(paste0('\n\n> Model MAE: `', round(model_mae, 4), '`\n\n'))
	cat(paste0('\n\n> Model Correaltion Between Actual & Predicted: `', round(model_correlation, 4), '`\n\n'))
	
	cat('\n\nMetrics from Test Data:\n\n')
	cat(codebc(defaultSummary(predicted_vs_actual)))
	
	cat('\n\nActual Observations:\n\n')
	cat(codebc(summary(predicted_vs_actual$obs)))
	
	cat('\n\nPredictios:\n\n')
	cat(codebc(summary(predicted_vs_actual$pred)))
	cat('\n\n')
	
	print(ggplot(data = predicted_vs_actual, mapping = aes(x = obs, y = pred)) +
		geom_point(alpha=0.2) + # alpha avoids overfiting
		geom_smooth(method = 'loess', se = TRUE, col='red', size=0.5) + # actual (A loess model fits a complicated curve through a set of points. In some ways, it can be thought of as a complicated moving average. It is the best possible curve (at least, for one sensible definition of best)) http://stats.stackexchange.com/questions/25092/what-is-the-difference-between-simple-linear-model-and-loess-model
		geom_smooth(method = 'lm', se = TRUE, col='black', size=0.5) + # regression
		labs(title = 'Predicted vs Observed',
			subtitle = 'Make sure there is a strong connection. Understand where the model isnt callibrated',
			caption = 'black == model; red == loess'))

	print(ggplot(data = predicted_vs_actual, mapping = aes(x = pred, y = residuals)) +
		geom_point(alpha=0.2) + # alpha avoids overfiting
		geom_smooth(method = 'loess', se = TRUE, col='red', size=0.5) + # actual (A loess model fits a complicated curve through a set of points. In some ways, it can be thought of as a complicated moving average. It is the best possible curve (at least, for one sensible definition of best)) http://stats.stackexchange.com/questions/25092/what-is-the-difference-between-simple-linear-model-and-loess-model
		#geom_smooth(method = 'lm', se = FALSE, col='black', size=0.5) + # regression
		labs(title = 'Residuals vs. Fit (i.e. predicted)',
			subtitle = 'Make sure there are no systematic patterns. Think of red line as a `moving average`.'))

	print(ggplot(data = predicted_vs_actual, mapping = aes(x = 1:nrow(predicted_vs_actual), y = residuals)) +
		geom_point(alpha=0.2) + # alpha avoids overfiting
		geom_smooth(method = 'loess', se = TRUE, col='red', size=0.5) + # actual (A loess model fits a complicated curve through a set of points. In some ways, it can be thought of as a complicated moving average. It is the best possible curve (at least, for one sensible definition of best)) http://stats.stackexchange.com/questions/25092/what-is-the-difference-between-simple-linear-model-and-loess-model
		#geom_smooth(method = 'lm', se = FALSE, col='black', size=0.5) + # regression
		labs(title = 'Lag (ordered) Plot of Residuals By Index',
			subtitle = 'The residuals should be independent. If independent, there should be no pattern or structure in the lag plot.',
			x = paste0('Residual Indexes 1-:',nrow(predicted_vs_actual)))) # http://www.itl.nist.gov/div898/handbook/pmd/section4/pmd444.htm

	#plot(density(predicted_vs_actual$residuals))
	fun_args <- list(mean = mean(predicted_vs_actual$residuals), sd = sd(predicted_vs_actual$residuals))
	print(ggplot(data = predicted_vs_actual, mapping = aes(x = residuals)) +
		geom_histogram(mapping=aes(y = ..density..), bins = 30) + # histogram of data
		geom_density(col = "red") + # emperical PDF
		stat_function(fun = dnorm, args = fun_args, col = "blue") + # theoretical normal PDF, based on data's mean & standard deviation
		coord_cartesian(xlim = c(-3, 3)) + 
		labs(title = 'Density Plot of Residuals',
			subtitle = 'assumption of *linear regression* is that residuals are `normal`',
			caption = 'red line is the emperiocal PDF; blue is theoretical normal PDF'))

	print(gg_qq_plot(data_vector = predicted_vs_actual$residuals, data_name = 'residuals'))

	#cat('\n\n')
	variable_importace <- varImp(model)
	#variable_importace <- data.frame(variable = rownames(variable_importace$importance), importance = variable_importace$importance$Overall)
	#variable_importace <- variable_importace %>% dplyr::select(variable, importance) %>% mutate(importance = round(importance, 1)) %>% dplyr::arrange(desc(importance))
	print(plot(variable_importace, top = 25))
	#print(kable(variable_importace))
	#cat(codebc(varImp(model)))
	
	return (c(model_rmse = model_rmse, model_mae = model_mae, model_correlation = model_correlation))
}
```

# Train Top Models on Entire Training Dataset & Predict on Test Set

```{r}
top_x_models <- 5
```

```{r echo = FALSE}
ggplot(data = df_target_long, mapping = aes(x = type,  y = target, group = type)) +
	geom_boxplot()
```

- Note: e.g. if there are rare values at the target extremes (lows/highs), the train and especially the test set might not be training/testing on them. Is the test set representative? If the test set doesn't have as extreme values, it can even predict better (e.g. lower RMSE higher Rsquared) than the average Cross Validation given on training because it's not using those extreme values.

```{r determine_best_models, echo = FALSE, comment='', results='asis'}
top_models <- resamples_means %>% 
	filter(metric == 'RMSE') %>% 
	mutate(rank = row_number(average)) %>% 
	filter(rank <= 5) %>% # LOWEST RMSE
	arrange(rank) %>% 
	dplyr::select(model, average) %>%
	dplyr::rename(cross_validation_rmse = average) %>%
	mutate(model_object = map(model, ~ { numeric_models[names(numeric_models) == .][[1]] })) # add models to data.frame so when we choose the top models later we will 


## TAKE THE 5 TOP MODELS (AND TUNING PARAMETERS THERE ARE ANY) AND RETRAIN ENTIRE TRAINING SET, AND PREDICT ON TEST SET
final_train_control <- trainControl(method = "none") # In cases where the model tuning values are known, train can be used to fit the model to the entire training set without any resampling or parameter tuning. Using the method = "none" option in trainControl can be used https://topepo.github.io/caret/model-training-and-tuning.html#fitting-models-without-parameter-tuning

model_stats <- map2(as.character(top_models$model), top_models$model_object, ~ {
	# model_name <- as.character(top_models$model)[[1]]
	# model_object <- top_models$model_object[[1]]
	model_name <- .x
	model_object <- .y

	cat(paste0('\n\n### ', model_object$modelInfo$label, ' (', model_name,')\n\n'))
	
	# get method, tuning grid, pre-processing steps.
	model_method <- model_object$method
	tune_grid <- model_object$bestTune

	if(is.null(model_object$preProcess$method))
	{
		pre_process <- NULL
	}else{
		pre_process_call <- as.character(model_object$call$preProc)
		pre_process <- pre_process_call[!(pre_process_call %in% c('c'))]
		
		cat(paste0('\n\nPre-Processing: `', paste(pre_process, collapse = ', '), '`\n\n'))
	}
	
	# if(!is.null(model_object$call$x) || !is.null(model_object$call$y)) { # if we used a non-formula
	# 
	# 	stopifnot(!is.null(model_object$call$x) && !is.null(model_object$call$y)) # if either is not null, both should be not null
	# 	non_formula_columns <- colnames(model_object$trainingData)
	# 	non_formula_columns <- non_formula_columns[-which(non_formula_columns == '.outcome')]
	# } else {

		training_column_names <- colnames(model_object$trainingData)
		model_formula_string <- paste(	'target ~', 
										paste0(training_column_names[-which(training_column_names == '.outcome')],
										collapse = ' + '))

		model_formula <- as.formula(model_formula_string)
	# }

	cat(paste0('\n\n> Model Formula: `', model_formula_string, '`\n\n'))
	
	if(!is.null(tune_grid) && nrow(tune_grid) == 1) {
		cat('\n\n```\n')
		walk2(colnames(tune_grid), as.character(tune_grid[1,]), ~ cat(paste0(.x,': ', .y, '\n')))
		cat('```\n')
	}

	if(refresh_models)
	{	
		set.seed(seed)
		# some models have different parameters for `train`, which we need to use when training the final model
		if(model_method == 'rf')
		{
			final_model <- train(
				form = model_formula,
				data = regression_train,
				method = model_method,
				trControl = final_train_control,
				preProc = pre_process,
				tuneGrid = tune_grid, 
				ntree = parameter_random_forest_ntree,
				importance = TRUE)

		}else if(model_method == 'cforest'){
			
			final_model <- train(
				form = model_formula,
				data = regression_train,
				method = model_method,
				trControl = final_train_control,
				preProc = pre_process,
				tuneGrid = tune_grid, 
				controls = cforest_unbiased(ntree = parameter_random_forest_ntree), importance = TRUE)

		}else if(model_method == 'avNNet' || model_method == 'nnet'){
			
			final_model <- train(
				form = model_formula,
				data = regression_train,
				method = model_method,
				trControl = final_train_control,
				preProc = pre_process,
				tuneGrid = tune_grid,
				linout = parameter_neural_network_linout,
				trace = parameter_neural_network_trace,
				MaxNWts = parameter_neural_network_max_num_weights,
				maxit = parameter_neural_network_max_iterations)

		}else if(model_method == 'treebag'){
			
			final_model <- train(
				form = model_formula,
				data = regression_train,
				method = model_method,
				trControl = final_train_control,
				preProc = pre_process,
				tuneGrid = tune_grid,
				nbagg = tuning_treebag_nbagg)

		}else{

			final_model <- train(
				form = model_formula,
				data = regression_train,
				method = model_method,
				trControl = final_train_control,
				preProc = pre_process,
				tuneGrid = tune_grid)
		}

		saveRDS(final_model, file = paste0('./regression_data/top_model_', model_name, '.RDS'))

	}else{

		final_model <- readRDS(file = paste0('./regression_data/top_model_', model_name, '.RDS'))
	}

	#cat(codebc(summary(final_model$finalModel)))
	model_stats <- model_plots(model = final_model, testing_set = regression_test)
	return (model_stats)
})

final_models_metrics <- data.frame(	model = factor(as.character(top_models$model),
									levels = as.character(top_models$model)),
									test_set_rmse = map_dbl(model_stats, ~ .['model_rmse']),
									cross_validation_rmse = top_models$cross_validation_rmse,
									mae = map_dbl(model_stats, ~ .['model_mae']),
									correlation = map_dbl(model_stats, ~ .['model_correlation']))

min_rmse <- min(final_models_metrics$test_set_rmse)
min_mae <- min(final_models_metrics$mae)
max_correlation <- max(final_models_metrics$correlation)

# prepare/format data for ggplot
final_models_metrics_long <- gather(final_models_metrics, metric, value, -model) %>%
	mutate(model = factor(model, levels = rev(unique(model))),
		type = ifelse(str_detect(metric, 'rmse'), str_split(metric, '_'), '')) %>%
	mutate(type = map_chr(type, ~ { 
			if(length(.) > 1)
			{
				return(paste0(.[1:2], collapse = ' '))
			}else{
				return ('test set')
			}
		}),
	metric = ifelse(str_detect(metric, 'rmse'), 'rmse', as.character(metric))) %>%
	mutate(metric = factor(metric, levels = unique(metric)))

best_values <- data.frame(metric = unique(final_models_metrics_long$metric), Z = c(min_rmse, min_mae, max_correlation))
ggplot(data = final_models_metrics_long, mapping = aes(x = model, y = value, col = type)) +
	geom_point() + 
	geom_hline(data = best_values, aes(yintercept = Z), color='red') +
	facet_grid(. ~ metric, scales = "free", space = "free_y") +
	coord_flip()
```
